\section{Scope}
Here a short review of Customers Line-up scope referred to what just stated in the RASD document.\\
Customer Line-Up is a crowdsourced application whose purpose is to create a service to support people, specially in lockdown time, in doing grocery shopping. Anyone can Line-up from his home in a specific supermarket simply opening Customer Line-up application. For each Line-up request, every Customer has only to select in which supermarket he intends to go and with which mean of transport. After that, the System shows to the Customer his Waiting Time and generates for him a QR code that has to be scanned at the entrance and the exit of the store.
Furthermore, the System retrieves the Customer’s position and computes the duration of the trip to the supermarket considering the current traffic situation and the mean of transport selected. In this way, the System can send to the Customer a notification when he has to start.
To let everyone to grocery shopping in a safe way, Customer Line-Up provides a fallback option for people who do not have access to the required technology. In fact, No-Tech Customers can be reported to the System by the Store Manager and can enter the store with a Ticket.\\
The software provide also a service to book a Visit in a specific Supermarket. The Customer uses the mobile phone interface to make a Booking Request indicating the involved supermarket, the date and time of the Visit and its Expected Duration. If the Customer is a Long-Term one, the system can mine this last parameter from previous data. Additionally, the Customer can indicate the exact list of items he intends to buy or their categories to enable the system to make a finer optimization allowing more people in the store. The system shows only dates and times when the supermarket is open and the number of its Bookings is lower than its capacity. It is important to underline that the system allows the Customer to make a single Booking Request at a time to permit a more fair distribution of the timeslots available. Also, for usage semplicity reasons, it permits only to cancel and not to modify the Request.\\
Finally, The system provides to the Store Managers a dedicated portal where they can check in real time the number of people inside their supermarket and the list of all the Bookings. Through this portal, they can report the entrances and the exits of No-Tech Customers.