\chapter{Installation Instructions}

\section{Install the Restful Server and the DB}

\begin{itemize}
\item Install MySQL Workbench 8.0 and MySQL Server.  
\item Take the file db clup.sql from the folder DatabaseAndConfiguration and execute it with MySQL Workbench to reproduce the database locally. 
\item Install Eclipse IDE. 
\item Import the CLuEJB and the CLupWEB as Eclipse project. Make sure to have the file tomee.xml in your Tomee configurations files with the correct username and password of MySQL. Also check to import into the project the eclipseLink.
\item Install Tomee Plume 8.0.3   
\item If you have any problems during these procedures you can find useful resolution tips in the guide, written by Professor Franternali, that you can find in the folder: DatabaseAndConfiguration.  
\item Start the server, simply by executing the CLupWEB project from Eclipse.
\item Moreover, if you do not want to install everything by yourself, we also offer the possibility to test the prototype directly on our server at: \\ "https://08a799d24d68.ngrok.io". 
\end{itemize}

 

\section{Install the Mobile Application}

For completeness, all the CLup tests are done in Android so we suggest you to test the application in this Environment. 

\subsection{Run the APK (Recommended)}
\begin{itemize}
\item In the delivery folder it is provided the APK of the application.
\item In the login page, just for the Acceptance test, there is a text input where you have to insert the address of your local server in your LAN and its port. For example, for us is: "http://192.168.1.10:8080".
\item Otherwise, you can test the applicatioin with our personal server at the address: "https://08a799d24d68.ngrok.io" as already stated.
\end{itemize}

\subsection{Run with Expo}
\begin{itemize}
\item Install expo on your pc with the instruction given from the documentation: 
"https://docs.expo.io/distribution/building-standalone-apps/"
\item Install the Application "Expo Go" on your smartphone.
\item Enter with your terminal in the folder CLupExpo.
\item Firstly, run the command "npm install --global expo-cli".
\item Then, run the command "npm start".
\item At this point you will see a web browser page to launch the application. Scan the QR code in your smartphone to download the app and try it.
\end{itemize}

 